Theorems and Definitions

### 2016-04-08 number_theory/hw/hw9.tex
finished number theory

\item Find a value of $n$ such that $\phi(n)/n < 1/4$. What do you think is a good strategy for
choosing $n$ so that $\phi(n)/n$ is close to zero?
\begin{quote}
One value for which this holds true is $n=210$. $\phi(210)$ is 48, and $48/210 = 8/35 < 1/4$. One
strategy for finding these numbers would be to
\end{quote}

@@

\item If $n$ is a positive integer prove that $\phi(n)=2$ if and only if $n\in\{ 3,4,6\}$.
\begin{quote}
$\Rightarrow)$
\noindent\\\\
$\Leftarrow)$ Suppose $n\in\{ 3,4,6\}$. Then $\phi(3)=2$, $\phi(4)=2$, and $\phi(6)=2$.
\end{quote}
\end{enumerate}
\end{document}

>>>>

\item Find a value of $n$ such that $\phi(n)/n < 1/4$. What do you think is a good strategy for
choosing $n$ so that $\phi(n)/n$ is close to zero?
\begin{quote}
One value for which this holds true is $n=210$. $\phi(210)$ is 48, and $48/210 = 8/35 < 1/4$. One
strategy for finding these numbers would be to pick values for which $\phi(n)$ is small but has
many unique prime factors.
\end{quote}

@@

\item If $n$ is a positive integer prove that $\phi(n)=2$ if and only if $n\in\{ 3,4,6\}$.
\begin{quote}
$\Rightarrow)$ Suppose $\phi(n)=2$ and let $k\in\ZZ > 2$ and $l\in\ZZ > 1$. We want to consider the
case where $n=2^k3^l$, so $\phi(n)=\phi(2^k3^l)=(2^k-2^{k-1})(3^l-3^{l-1})$. This can be further
simplified to $2^k(1/2)3^l(2/3)=2^k3^l(1/3)>2$ for $l>1$ and $k>2$. Therefore we only have
$\{ 1,2,3,4,6,12 \}$ to consider. Since $\phi(1)=\phi(2)=1$ and $\phi(12)=4$, we can eliminate
those values. However, $\phi(3)=\phi(4)=\phi(6)=2$, so $\phi(n)=2$ when $n\in\{ 3,4,6\}$.
\noindent\\\\
$\Leftarrow)$ Suppose $n\in\{ 3,4,6\}$. Then $\phi(3)=2$, $\phi(4)=2$, and $\phi(6)=2$.
\end{quote}
\end{enumerate}
\end{document}
